---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fwdSlash

<!-- badges: start -->
<!-- badges: end -->

## Overview

The `fwdSlash` package provides a number of add-ins that extend the capabilities of RStudio. The motivation for this package is an add-in that allows you to paste file paths into RStudio from a Windows machine. This will usually mean replacing backslashes (`\`) with forwardslashes (`/`)---hence the name `fwdSlash`---.

The package also includes others add-ins that perform other special copy/pastes, as well as some add-ins for working with hard-coded vectors.

<!-- * An add-in to copy a file path in R and convert it into a system (Windows) file path. -->
<!-- * An add-in to paste the hard-code for a vector based on the current selection. -->
<!-- * An add-in the evaluate the code currenlty selected in RStudio and replace it with a hard-coded vector. -->
<!-- * An add-in to evaluate the code currenlty selected in RStudio and put the output into the clipboard. -->

For more see `help("file_path_add-ins")` and `help("vector_code_add-ins")`. Note that the paste add-ins will not change the clipboard itself, they will simply insert text to the current location leaving the clipboard untouched.


## Installation

You can install the `fwdSlash` package from [GitHub](https://github.com/t-gummer/fwdSlash) with:

``` r
# install.packages("devtools")  #In case you have not installed it.
devtools::install_github("t-gummer/fwdSlash")
```

Once you have done this, the add-ins will be available in RStudio for use in all future R sessions.


## Included Add-ins


The `fwdSlash` package contains the following add-ins:

```{r, echo=FALSE, warning=FALSE}
# install.packages("kableExtra")
library(kableExtra)
library(magrittr)
table_header <- c("Add-in Name","Underlying R Function","Recommended Shortcut","Description")
table_content <- c("Set default keyboard shortcuts","`set_shortcuts_default()`","_none_","Click on this add-in in RStudio to set the shortcuts for the other add-ins below.",
                   "Special copy (file path)","`copy_file_path()`","`Ctrl+Alt+C`","Copy a file path to the clipboard so that it will work as a Windows file path.",
                   "Special paste (file path)","`paste_file_path()`","`Ctrl+Shift+V`","Paste a file path in the clipboard so that it will work as an R file path (this does _not_ change the clipboard).",
                   "Special paste (vector code)","`paste_vector_code()`","`Ctrl+H`","Pastes the current text in the clipboard as R code for a hard-coded vector using the `c()` function (this does _not_ change the clipboard).",
                   "Hard code vector","`hard_code_vector_code()`","`Ctrl+Alt+H`","Evaluate the current selected code in RStudio and replace it with a hard-coded vector.",
                   "Special copy (R evaluation)","`copy_r_eval()`","`Ctrl+G`","Evaluate currently selected code in RStudio and copy the output to the clipboard (one line per element of vectors). This can be thought of as reversing the \"_Special paste (vector code)_\" add-in."
                   )
table_content %>% 
  matrix(ncol = 4,byrow = TRUE,dimnames = list(NULL,table_header)) %>% 
  kable(format = "markdown",align = "c")

```

The decisions for the "recommended shortcuts" are based on both availability (they do not overwrite any of the existing default ones) and some attempt at logical conventions.
<!-- Rationalise each choiceof shortcut below -->

## Workflow

It is recommended that you set the fwdSlash `Special paste (file path)` add-in as a keyboard shortcut to allow for easy access. `Ctrl+Shift+V` is a good option for it's similarity to `Ctrl+V`.

* [Keyboard Shortcuts](https://rstudio.github.io/rstudioaddins/#keyboard-shorcuts)
* [Customizing Keyboard Shortcuts](https://support.rstudio.com/hc/en-us/articles/206382178-Customizing-Keyboard-Shortcuts)


This workflow is much improved compared to the usual (slow) alternative, which is of doing a _find and replace_ (or worse, manually replacing all the backslashes with forward slashes).

<!-- There is a function in the fwdSlash package that allows you to easily change the RStudio keyboard shortcut _programmatically_ as an alternative to clicking through menus. -->

## Compatability

`fwdSlash` was built for use on a Windows operating system.

It also has the potential to work on Mac or Linux by vitue of the [`clipr`](https://www.r-pkg.org/pkg/clipr) package. It is however less useful on these operating systems than Windows due to the fact that their file paths are generally do not require any modification to be recognised in R.

## Similar packages

There are a number of other packages that provide useful tools for accessing the keyboard. Some examples are listed below.

* [`clipr`](https://www.r-pkg.org/pkg/clipr)
* [`imageclipr`](https://github.com/Timag/imageclipr)
* [`datapasta`](https://github.com/MilesMcBain/datapasta)
